Imputation of Incomplete Multilevel Data with \pkg{mice}

### 2022-06-21 Manuscript/Imputation_of_Incomplete_Multilevel_Data.Rmd
Make forest plot dependent on sample size

@@

@@

@@

[TODO: think about introducing systematically missing hiv.]

@@

@@

```{r forest, echo=FALSE}
fits <-
  purrr::map_dfr(
    unique(impact$name),
    ~ {
      glm(
        mort ~ 1 + age + motor_score + pupil + ct,
        family = "binomial",
        data = filter(impact, name == .x)
      )
    } %>%
      broom::tidy(conf.int = TRUE, exponentiate = TRUE) %>%
      .[, c("term", "estimate", "conf.low", "conf.high")] %>%
      cbind(name = as.character(.x), .)
  )
filter(fits, term %in% c("ctIII")) %>% #, "ctIV/V"
  ggplot(aes(y = name, x = estimate)) +
  geom_vline(xintercept = 1, size = 1.5, color = "grey95") +
  geom_point() +
  geom_linerange(aes(y = name, xmin = conf.low, xmax = conf.high)) +
  labs(y = "Study", x = "Adjusted odds ratio for ct", color = NULL) +
  theme_classic()
# TODO: add heterogeneity in distribution of ct -> prevalence in ct across clusters with CI
# TODO: missingness prop inside clusters
# TODO: make row height proportional to pattern frequency
```
<!-- We will use the following estimates as comparative truth in this tutorial: -->
```{r truth}
# fit <- glmer(mod, family = "binomial", data = impact) # fit the model
# tidy(fit, conf.int = TRUE, exponentiate = TRUE)       # print estimates
```

>>>>

[TODO: explain case study]

@@

### Imputation with multilevel model

```{r pop_multilevel, message=FALSE, warning=FALSE}
# adjust the predictor matrix
pred["popular", "school"] <- -2 
plot_pred(pred)

@@

[TODO: change the order of case study 2 and 3]

@@

@@

[TODO: check if there is systematic missingness in this dataset, if not make Marshall Computerized Tomography classification (ct) systematically missing.]

@@

```{r forest, echo=FALSE}
fits <-
  purrr::map_dfr(
    unique(impact$name),
    ~ {
      glm(
        mort ~ 1 + age + motor_score + pupil + ct,
        family = "binomial",
        data = filter(impact, name == .x)
      )
    } %>%
      broom::tidy(conf.int = TRUE, exponentiate = TRUE) %>%
      .[, c("term", "estimate", "conf.low", "conf.high")] %>%
      cbind(name = as.character(.x), .)
  ) %>% filter(term %in% c("ctIII", "ctIV/V"))

n <- impact %>% group_by(name) %>% 
  tally()

fits %>% left_join(n, by = "name") %>% 
  ggplot(aes(y = name, x = estimate, color = term, size = n)) +
  geom_vline(xintercept = 1, size = 1.5, color = "grey95") +
  geom_linerange(aes(y = name, xmin = conf.low, xmax = conf.high, size = 0.5), position = position_dodge(width = 0.5)) +
  geom_point(shape = 20, position = position_dodge(width = 0.5)) +
  labs(y = "Study", x = "Adjusted odds ratio for ct", color = NULL) +
  theme_classic() +
  scale_size(guide = 'none')
# TODO: add heterogeneity in distribution of ct -> prevalence in ct across clusters with CI
# TODO: missingness prop inside clusters
# TODO: make row height proportional to pattern frequency
```
<!-- We will use the following estimates as comparative truth in this tutorial: -->
```{r truth}
# fit <- glmer(mod, family = "binomial", data = impact) # fit the model
# tidy(fit, conf.int = TRUE, exponentiate = TRUE)       # print estimates
```

[TODO: show how much variance there is after different methods]

### 2022-06-21 Manuscript/Imputation_of_Incomplete_Multilevel_Data.tex
Make forest plot dependent on sample size

@@

             Estimate Std.Error   t.value        df   P(>|t|)       RIV       FMI 
(Intercept)     3.469     0.139    24.958    32.413     0.000     0.542     0.388 
sex             1.128     0.167     6.744    22.962     0.000     0.716     0.462 
texp            0.102     0.011     9.237    11.848     0.000     1.387     0.637 
sex:texp       -0.018     0.011    -1.616    16.878     0.125     0.949     0.538

                            Estimate 
Intercept~~Intercept|school    0.150 
sex~~sex|school                0.143 
Intercept~~sex|school          0.002 
Residual~~Residual             0.677 
ICC|school                     0.182

@@

             Estimate Std.Error   t.value        df   P(>|t|)       RIV       FMI 
(Intercept)     3.369     0.163    20.666    17.473     0.000     0.917     0.529 
sex             1.228     0.178     6.910    44.805     0.000     0.426     0.328 
texp            0.105     0.012     8.713    10.517     0.000     1.609     0.673 
sex:texp       -0.027     0.011    -2.416    57.000     0.019     0.360     0.289

                            Estimate 
Intercept~~Intercept|school    0.178 
sex~~sex|school                0.255 
Intercept~~sex|school         -0.036 
Residual~~Residual             0.628 
ICC|school                     0.220

@@

@@

{[}TODO: think about introducing systematically missing hiv.{]}

@@

@@

>>>>

{[}TODO: explain case study{]}

@@

             Estimate Std.Error   t.value        df   P(>|t|)       RIV       FMI 
(Intercept)     3.436     0.179    19.207    11.230     0.000     1.480     0.653 
sex             1.210     0.208     5.812    13.898     0.000     1.157     0.591 
texp            0.101     0.014     7.261     7.456     0.000     2.738     0.784 
sex:texp       -0.020     0.017    -1.153     7.534     0.284     2.686     0.780

                            Estimate 
Intercept~~Intercept|school    0.158 
sex~~sex|school                0.212 
Intercept~~sex|school         -0.026 
Residual~~Residual             0.663 
ICC|school                     0.188

@@

             Estimate Std.Error   t.value        df   P(>|t|)       RIV       FMI 
(Intercept)     3.361     0.177    18.967    16.581     0.000     0.965     0.543 
sex             1.250     0.243     5.145     9.696     0.000     1.796     0.699 
texp            0.105     0.014     7.425     8.751     0.000     2.087     0.731 
sex:texp       -0.026     0.019    -1.388     6.889     0.208     3.202     0.810

                            Estimate 
Intercept~~Intercept|school    0.216 
sex~~sex|school                0.240 
Intercept~~sex|school         -0.045 
Residual~~Residual             0.615 
ICC|school                     0.259

\hypertarget{imputation-with-multilevel-model}{%
\subsubsection{Imputation with multilevel
model}\label{imputation-with-multilevel-model}}

\begin{CodeChunk}
\begin{CodeInput}
R> # adjust the predictor matrix
R> pred["popular", "school"] <- -2 
R> plot_pred(pred)
\end{CodeInput}

\begin{center}\includegraphics{Imputation_of_Incomplete_Multilevel_Data_files/figure-latex/pop_multilevel-1} \end{center}

             Estimate Std.Error   t.value        df   P(>|t|)       RIV       FMI 
(Intercept)     3.333     0.177    18.832    16.459     0.000     0.972     0.545 
sex             1.356     0.193     7.014    37.019     0.000     0.490     0.362 
texp            0.106     0.012     8.870    13.221     0.000     1.222     0.606 
sex:texp       -0.034     0.012    -2.901    51.319     0.005     0.387     0.306

                            Estimate 
Intercept~~Intercept|school    0.213 
sex~~sex|school                0.307 
Intercept~~sex|school         -0.084 
Residual~~Residual             0.622 
ICC|school                     0.254

@@

{[}TODO: change the order of case study 2 and 3{]}

@@

@@

{[}TODO: check if there is systematic missingness in this dataset, if
not make Marshall Computerized Tomography classification (ct)
systematically missing.{]}

@@

{[}TODO: show how much variance there is after different methods{]}
